Persistence in functional topology: local-connectivity, q-tameness and a correction to a theorem of Morse

### 2021-04-15 main.tex
Updates from Overleaf

\begin{abstract}
	During the 1930's Morse developed a general theory, which he called functional topology, relating the critical set of a semi-continuous functional and the topology of its sublevel sets, and, in join work with Tompkins, used this theory to study minimal surfaces.
	Many of the key insights of functional topology have been rediscovered in the study of persistence homology.
	In particular, conditions enforcing the existence of an interval decomposition are as central to functional topology as they are to persistence theory.
	With modern applications to geometry in mind, in this article we present a comprehensive and up-to-date study of the most delicate of these conditions: local-connectivity. Providing, on passing, a correction to the Critical Surface Theorem of Morse and Tompkins.
\end{abstract}

>>>>

\begin{abstract}
	During the 1930's Morse developed a general theory, which he named functional topology, relating the critical set of a semi-continuous functional and the topology of its sublevel sets; and, in joint work with Tompkins, used this body of work to study minimal surfaces.
	Many of the key insights of functional topology have been rediscovered in the study of persistence homology.
	In particular, conditions enforcing the existence of an interval decomposition are as central to functional topology as they are to persistence theory.
	With modern applications to geometry in mind, in this article we present a comprehensive and up-to-date study of local-connectivity for Morse filtrations, the most delicate of these conditions, and provide in passing a correction to the Critical Surface Theorem of Morse and Tompkins.
\end{abstract}
